A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-30 journal/relatedwork.tex
related
ready to finish response

@@

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines, and is perhaps most similar to ours in assumptions. In particular we agree with ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  However, while we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults. Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

@@

@@

>>>>

\subsection{Fuzzer Taming/Bug Triage}

@@

\subsection{Fault Localization}

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Many fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,MetalSelect,Papadakis,MechLocal,MurtazaTrace,Musco}.
One  core aspect of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.

The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines, and is perhaps most similar to ours in assumptions. In particular we agree with ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  However, while we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults. Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

Metallaxis \cite{Metallaxis,MetalSelect,Papadakis}, in contrast to MUSE/MUSEUM (and our own work), relies on the idea that mutants that are (relative to other killed mutants) mostly killed by failing tests likely have a connection to a program defect or defects.  This idea relies on a fundamentally different notion of ``killing'' a mutant than the one primarily used in this paper.  We generally speak of a mutant being killed when the mutant makes a previously passing test fail; in this sense, a failing test cannot kill a mutant.  However, these ``correctness kills'' are not the only possible notion of mutant kill used in the literature; a different approach is to consider a mutant killed whenever it produces a different output than the original program.  This point of view, unfortunately, is not obviously useful for compiler mutants, where almost all mutants, however benign, of covered code, will result in some (perhaps meaningless) change in the output binary.  We have therefore consider a mutant killed only when it causes semantically wrong output from a compiled program, a fairly complex specification-based notion of difference.  Compilers may therefore be an unusually poor fit for the Metallaxis approach, which, as our results above show, is quite competitive for more ``normal'' localization, where output (vs. specification-satisfaction/correctness) differences are likely to be meaningful.  Extending our approach beyond ``correctness kills'' (at least for non-compiler contexts) is an interesting possible line of future research.

Musco, Monperrus, and Preux offer yet another alternative mutant-based approach to localization, one that (like ours) is explicitly causal \cite{Musco}.  Their approach, quite different than MUSE, MUSEUM, Metallaxis, or our own, uses mutants to mark likely causal relationships in call graphs.  A recent survey of advances in mutation testing places all of these approaches using mutants in fault localization within the larger context of mutation testing research \cite{MutationSurvey}.

@@

\subsection{Automated Program Repair}

@@

\subsection{Distance Metrics}
